Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-21 paper.tex
check

When then prove that, for any instance $C$ of the Cast ADT, \effCEK{C}
is equivelent to \ineffCEKD{] provided that $C$ satisfies a collection
of properties that we call the Lazy D Cast abstract data type.
In Section~\ref{sec:hypercoercion-correctness} we show that
the \lazyD{} hypercoercions $H$ are an instance of the Lazy D ADT,
and therefore \effCEK{H} is equivalent to \ineffCEKD{}.

>>>>

We prove that, for any instance $C$ of the Cast ADT, \effCEK{C} is
equivelent to \ineffCEKD{] provided that $C$ satisfies a collection of
properties that we call the Lazy D Cast abstract data type.  In
Section~\ref{sec:hypercoercion-correctness} we show that the \lazyD{}
hypercoercions $H$ are an instance of the Lazy D ADT, and therefore
\effCEK{H} is equivalent to \ineffCEKD{}.
